NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-08-24 ms_nihao_budget.tex
compare with simulation works

The trends of each component fraction are similar, in that  the
fractions are relatively low in low mass haloes, and increase as the
halo mass increases.  The main difference between the different
components is the slope, with the baryonic mass fraction having a
shallower slope than the stellar mass fraction.  This is because in
low mass haloes ($\Mhalo\sim 10^{10}\Msun$) most of the baryons are in
the form of gas, while in the highest mass haloes we study
($\Mhalo\sim 10^{12}\Msun$) {\bf a substantial amounts of gas
forms stars}.
{\bf To compare with baryon fraction in \citet{Voort16}, we derive
the M$_{500}$ and R$_{500}$ to recalculate the ratio between 
baryon fraction to the universal fraction of baryons. The baryon
fraction have good agreement with each other in the whole mass range
where NIHAO simulations explored. For the massive haloes with 
M$_{500} > 10^{12} \Msun$, there are two galaxies from NIHAO have
reduced baryon fraction and four more massive galaxies from FIRE
have larger reduced baryon fraction which may hint that the baryon
fraction will decrease as the halo mass increases in large mass range.}

@@

%% FIGURE 3
\begin{figure}
\centerline{
  \psfig{figure=ratioprofile.eps,width=0.5\textwidth}
}
\caption{Baryon distribution of each galaxy from NIHAO simulations. 
 The lines are colour coded by their halo mass, which shows a
  clear trend that the more massive haloes preserve more baryons at
  all radii.}
\label{fig:rps}
\end{figure}

@@

\subsection{Comparison with Observations of Milky Way mass haloes}
{\bf Observations can gain information of CGM from absorption lines
and emission lines. Although emission lines allow us to direct obtain
a 3D picture of the distribution of gas in the CGM, emission line studies
preferentially probe the dense gas closer to galaxies since gas 
emissivity scales with the square of density. The situation is changing
by building current facilities, e.g.\citet{Hayes16}, absorption line,
however, is the most common observational constraints on the physical
state of the CGM.}
The COS-HALOs survey is
filling in details about the $z \sim 0$ CGM \citep{Peeples14,
  Tumlinson11, Tumlinson13, Werk12, Werk13, Werk14}.  For the CGM of
low-redshift $\sim L^*$ galaxies ($\Mstar\sim 10^{10.5}\Msun$),
\citet{Tumlinson13} and \citet{Peeples14} constrain the mass of  the
warm-hot CGM ($T \sim 10^{5-7}$K), \citet{Werk14} provides a strict
lower limit to the mass of cool material ($T \sim 10^{4-5}$K) in the
CGM of these galaxies.  In a study using X-rays,  \citet{Anderson13}
place a constraints on the mass of  hot gas ($T > 10^7$K) residing in
the extended hot halos.

@@

The observations and the simulations match well in every phase except
 the cool CGM gas, where the observations find $3\times$ the
mass that simulations predict.  If the observations are correct, the
simulations have either ejected cool gas too far, or  they have
created a CGM with the wrong mix of gas temperatures. The total gas
fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the latter
option.   However, \citet{Stern16} developed a new method to
constrain the physical conditions in the cool CGM from measurements
of ionic  columns densities. This new method combines the
information available from different sightlines during the photoionization
modeling, and was applied to the COS-HALOs data,  yielding a total
cool CGM mass within the virial radius of $1.3\times10^{10}\Msun$
which is shown by the green hashed bar in Fig~\ref{fig:budget} and
is in good agreement with our prediction.  As the
Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the cool gas is
the most important component {\bf for most galaxies in NIHAO simulation
($10^{10} < M/\Msun < 10^{12}$), the cold and hot gas only dominate for
galaxies at lower and higher mass end in NIHAO suite.} The more accurate
knowledge of the physical properties of CGM are necessary to better
understand the role of the CGM in galaxy formation.
%
As the CGM of lower mass galaxies will soon be observed,
Table~\ref{tab:comparison} lists information about CGM
mass fractions of the different components of gas in haloes down to a
halo mass of $\sim 10^{10}\Msun$.

@@

@@

%
\bibitem[Ford et al.(2015)]{Ford15} Ford, A.~B., Werk, J.~W., Dav{\`e}, R., et al.\ 2015, arXiv:1503.02084

>>>>

The trends of each component fraction are similar, in that  the
fractions are relatively low in low mass haloes, and increase as the
halo mass increases.  The main difference between the different
components is the slope, with the baryonic mass fraction having a
shallower slope than the stellar mass fraction.  This is because in
low mass haloes ($\Mhalo\sim 10^{10}\Msun$) most of the baryons are in
the form of gas, while in the highest mass haloes we study
($\Mhalo\sim 10^{12}\Msun$) {\bf a substantial amounts of gas
forms stars}.

{\bf \citet{Christensen16} run twenty galaxy simulations spanning the mass range
from $10^{9.5} - 10^{12} \Msun$ using zoom-in cosmological hydrodynamic 
simulation code and didn't only reproduce the stellar mass - halo mass
relation but also showed a similar baryon fraction relation, e.g. in 
L$^*$ galaxies, the fraction is reduced by 20\% while in galaxies with
halo mass $< 10^{10} \Msun$ there can be as large as an 80\% mass reduction.
This suggests that the potential well of the halo regulates the baryon
fraction.
To compare with baryon fraction in \citet{Voort16}, we derive
the M$_{500}$ and R$_{500}$ to recalculate the ratio between 
baryon fraction to the universal fraction of baryons. The baryon
fraction have good agreement with each other in the whole mass range
where NIHAO simulations explored. For the massive haloes with 
M$_{500} > 10^{12} \Msun$, there are two galaxies from NIHAO have
reduced baryon fraction and four more massive galaxies from FIRE
have larger reduced baryon fraction which may hint that the baryon
fraction will decrease as the halo mass increases in large mass range.}

@@

{\bf Two cosmological hydrodynamic simulations in \citet{Ford15} 
which employed two prescriptions for galactic 
outflow models to compare with COS-Halos showed this cumulative
baryon fraction profile for COS-Halos matched sample of galaxies.
One hybrid energy/momentum driven winds model ("ezw" model) makes up to
65\% of all baryons inside the halo. This is broadly consistent with
estimates of baryonic mass derived from \citet{Werk14} and our 
finding in Fig.~\ref{fig:budget}. Comparing the cumulative baryon
fraction profile in detail, Fig.10 in \citet{Ford15} shows the baryon
fraction within 0.1$\Rvir$ is only $\sim 30\%$ and the fraction 
gradually increases to 65\% at $\Rvir$ while the profile of galaxies
with halo mass below $10^{11} \Msun$ in Fig.~\ref{fig:rps} have 
similar feature, the more massive galaxies all have roughly flat slopes.
The simplified outflow model (constant wind model or "cw" model) shows
lower fraction at all radii inside $\Rvir$ even though "ezw" model
and "cw" model generally gives similar observational absorption 
line properties. This suggests that the profile of cumulative baryon
fraction, as a complementary of total amount observation of CGM,
 is important to distinguish between competing outflow models
that often closely relate to the feedback models.
}
%% FIGURE 3
\begin{figure}
\centerline{
  \psfig{figure=ratioprofile.eps,width=0.5\textwidth}
}
\caption{Baryon distribution of each galaxy from NIHAO simulations. 
 The lines are colour coded by their halo mass, which shows a
  clear trend that the more massive haloes preserve more baryons at
  all radii.}
\label{fig:rps}
\end{figure}

@@

\subsection{Comparison with observations
of Milky Way mass haloes}

{\bf Observations can gain information of CGM from absorption lines
and emission lines. Although emission lines allow us to direct obtain
a 3D picture of the distribution of gas in the CGM, emission line studies
preferentially probe the dense gas closer to galaxies since gas 
emissivity scales with the square of density. The situation is changing
by building current facilities, e.g.~\citet{Hayes16}, absorption line,
however, is the most common observational constraints on the physical
state of the CGM.}
The COS-HALOs survey is
filling in details about the $z \sim 0$ CGM \citep{Peeples14,
  Tumlinson11, Tumlinson13, Werk12, Werk13, Werk14}.  For the CGM of
low-redshift $\sim L^*$ galaxies ($\Mstar\sim 10^{10.5}\Msun$),
\citet{Tumlinson13} and \citet{Peeples14} constrain the mass of  the
warm-hot CGM ($T \sim 10^{5-7}$K), \citet{Werk14} provides a strict
lower limit to the mass of cool material ($T \sim 10^{4-5}$K) in the
CGM of these galaxies.  In a study using X-rays,  \citet{Anderson13}
place a constraints on the mass of  hot gas ($T > 10^7$K) residing in
the extended hot halos.

@@

The observations and the simulations match well in every phase except
 the cool CGM gas, where the observations find $3\times$ the
mass that simulations predict.  If the observations are correct, the
simulations have either ejected cool gas too far, or  they have
created a CGM with the wrong mix of gas temperatures. The total gas
fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the latter
option.   However, \citet{Stern16} developed a new method to
constrain the physical conditions in the cool CGM from measurements
of ionic  columns densities. This new method combines the
information available from different sightlines during the photoionization
modeling, and was applied to the COS-HALOs data,  yielding a total
cool CGM mass within the virial radius of $1.3\times10^{10}\Msun$
which is shown by the green hashed bar in Fig~\ref{fig:budget} and
is in good agreement with our prediction.  As the
Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the cool gas is
the most important component {\bf for most galaxies in NIHAO simulation
($10^{10} < M/\Msun < 10^{12}$), the cold and hot gas only dominate for
galaxies at lower and higher mass end in NIHAO suite.} 
{\bf A new estimation for the baryonic fractions from a set of
eight Milky Way-sized zoom-in cosmological simulations 
\citep{Colin16} is genenrally consistence with our results. The 
fraction of cool gas from their simulation is even lower 
($f_{\rm cool}$ = 0.034) than ours and the result from 
\citet{Stern16}. On the other hand, \citet{Peeples14} gave 
a conservative observational estimate about warm-hot gas and
showed that the fraction of gas in this phase is only 5\%, 
which is the lower limit of the estimates from \citet{Werk14} 
and less than the average values from \citet{Colin16} 
($f_{\rm warm-hot} \approx 24\%$) and our finding 
($f_{\rm warm-hot} \approx 17\%$). Therefore, the mix temperature
of CGM have large uncertainty and}
the more accurate
knowledge of the physical properties of CGM are necessary to better
understand the role of the CGM in galaxy formation.
%
As the CGM of lower mass galaxies will soon be observed,
Table~\ref{tab:comparison} lists information about CGM
mass fractions of the different components of gas in haloes down to a
halo mass of $\sim 10^{10}\Msun$.

@@

%In-N-Out: The Gas Cycle from Dwarfs to Spiral Galaxies
\bibitem[Christensen et al.(2016)]{Christensen16}
Christensen, C.~R., Dav{\'e}, R., Governato, F., et al.\ 2016, \apj, 824, 57

%Cosmological simulations of Milky Way-sized galaxies
\bibitem[Colin et al.(2016)]{Colin16}
Colin, P., Avila-Reese, V., Roca-Fabrega, S., et al.\ 2016, \apj, in press

@@

%
\bibitem[Ford et al.(2015)]{Ford15} Ford, A.~B., Werk, J.~W., Dav{\`e}, R., et al.\ 2016, \mnras, 459, 1745
